Dynamical modeling of tidal streams

### 2014-01-07 tex/ms.tex
streams: move a figure, remove a galpy link
streams: add link

The full modeling and action--angle framework presented here is
available as part of the \emph{galpy} Galactic Dynamics
code\footnote{Available at
  \protect{\url{http://github.com/jobovy/galpy}}~.}. A tutorial on how
to use this code is given at
\[
\protect{\mathrm{\url{http://jobovy.github.io/galpy/}}}\,.
\]
BOVY:WRITE AND LINK TO TUTORIAL.

@@

The action--angle method described in this Appendix is implemented in
the \emph{galpy} Galactic dynamics code\footnote{Available at
  \protect{\url{http://github.com/jobovy/galpy}}~.}.

>>>>

The full modeling and action--angle framework presented here is
available as part of the \emph{galpy} Galactic Dynamics
code\footnote{Available at
  \protect{\url{http://github.com/jobovy/galpy}}~.}. A tutorial on how
to use this code is given at
\[
\protect{\mathrm{\url{http://jobovy.github.io/galpy/streamdf.html}}}\,.
\]

@@

The action--angle method described in this Appendix is implemented in
the \emph{galpy} Galactic dynamics code.
